Quasars Probing Quasars IX. Probing the Circumgalactic Flows of Quasars [v1.1]

### 2017-02-09 QPQ9/qpq9_draft.tex
small changes

From our QPQ survey\footnote{http://www.qpqsurvey.org} (QPQ1), we have analyzed 195~systems 
that pass within 300\,kpc physical from a foreground quasar with $z > 1.6$. We restrict the sample 
to foreground quasars with redshift measured from \ion{Mg}{2}, [\ion{O}{3}], H$\alpha$, or 
H$\beta$ emission, giving a precision of $400\,{\rm km\,s^{-1}}$ or lower. [\ion{O}{3}] has the 
smallest dispersion of $44\,{\rm km\,s^{-1}}$ about the systemic redshift, and we analyze the 
sub-sample with [\ion{O}{3}] redshifts separately. The [\ion{O}{3}] line has an average blueshift 
of $27\,{\rm km\,s^{-1}}$ about the systemic redshift, which has been added when we compute the 
redshift of the line. Systemic redshifts measured from \ion{Mg}{2} have a precision of 
$272\,{\rm km\,s^{-1}}$, and we have taken into account the median redshift of 
$97\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from [\ion{O}{3}] \citep{Richards+02}. In QPQ8 we have 
quantified the precision of H$\alpha$ and H$\beta$ to be 
$300\,{\rm km\,s^{-1}}$ and $392\,{\rm km\,s^{-1}}$ respectively. 
\citep{hewittwild}.
We include only those spectra with S/N~$> XX$\AA\ at the
observed wavelengths of lya, \ion{C}{2}~1334, or 
\ion{C}{4}~1548 transitions.  Of the ntot~sightlines, 
nhigh\ have spectral resolution ~$> 5,000$ from echellette
or echelle observations (QPQ8).  This high-dispersion 
sample is analyzed [separately] throughout the paper.
Figure~\ref{fig:exp} summarizes the experimental design.
Refer to previous QPQ
publications for details on data reduction
and continuum normalzaton (QPQ6, QPQ7, QPQ8).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analysis}
\label{sec:analysis}

@@

JXP and ML acknowledge support from the National
Science Foundation (NSF) grant AST-1010004 and AST-XX. 
JXP thanks the Alexander
von Humboldt foundation for a visitor fellowship to the MPIA where
part of this work was performed, as well as the staff at MPIA for
their hospitality during his visits.
JFH acknowledges generous support from the Alexander von Humboldt
foundation in the context of the Sofja Kovalevskaja Award. The
Humboldt foundation is funded by the German Federal Ministry for
Education and Research.

%Much of the data presented herein were obtained at the W.M. Keck
%Observatory, which is operated as a scientific partnership among the
%California Institute of Technology, the University of California, and
%the National Aeronautics and Space Administration. The Observatory was
%made possible by the generous financial support of the W.M. Keck
%Foundation.  Some of the Keck data were obtained through the NSF
%Telescope System Instrumentation Program (TSIP), supported by AURA
%through the NSF under AURA Cooperative Agreement AST 01-32798 as
%amended.
%
%Some of the data herein were obtained at the Gemini Observatory, which
%is operated by the Association of Universities for Research in
%%Astronomy, Inc., under a cooperative agreement with the NSF on behalf
%of the Gemini partnership: the NSF (United
%States), the Science and Technology Facilities Council (United
%Kingdom), the National Research Council (Canada), CONICYT (Chile), the
%Australian Research Council (Australia), Minist\'{e}rio da
%Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil) and Ministerio de
%Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina). 
%
%The authors wish to recognize and acknowledge the very
%significant cultural role and reverence that the summit of Mauna Kea
%has always had within the indigenous Hawaiian community. We are most
%fortunate to have the opportunity to conduct observations from this
%mountain.
%Acknowledge TK Chan. CP Choi.

>>>>

Our primary scientific interest is to measure the average velocity fields of the C$^+$, C$^{3+}$, 
and Mg$^+$ absorption associated with the CGM of the massive galaxies hosting $z\sim 2.4$ quasars.

From our QPQ survey\footnote{http://www.qpqsurvey.org} (QPQ1), we have analyzed a subset of 195 
systems that pass within 300\,kpc physical from a foreground quasar with $z > 1.6$. We restrict
 the sample to foreground quasars with redshift measured from \ion{Mg}{2}\,2800, 
[\ion{O}{3}]\,5007, H$\alpha$, or H$\beta$ emission, giving a precision of 
$400\,{\rm km\,s^{-1}}$ or lower. 
%#[\ion{O}{3}] has the smallest dispersion of $44\,{\rm km\,s^{-1}}$ about the systemic redshift, 
%and we analyze the sub-sample with [\ion{O}{3}] redshifts separately. 
The [\ion{O}{3}] line has an average blueshift of $27\,{\rm km\,s^{-1}}$ about the systemic 
redshift \citep{Boroson05}, which has been added when we compute the 
redshift of the line. Systemic redshifts measured from \ion{Mg}{2} have a precision of 
$272\,{\rm km\,s^{-1}}$, and we have taken into account the median redshift of 
$97\,{\rm km\,s^{-1}}$ of \ion{Mg}{2} from [\ion{O}{3}] \citep{Richards+02}. In QPQ8. we have 
quantified the precision of H$\alpha$ and H$\beta$ to be 
$300\,{\rm km\,s^{-1}}$ and $392\,{\rm km\,s^{-1}}$ respectively. 
%\citep{HewittWild10}. 
Of the 195 sightlines, 13 have spectral resolution $> 5000$ from echellette or echelle 
observations. This high-dispersion sample has been analyzed separately in QPQ8. 
Figure~\ref{fig:experiment} summarizes the experimental design. We refer the reader to previous 
QPQ publications for the redshift centroiding algorithm, and details on data reduction and 
continuum normalization (QPQ6, QPQ8).

As in the previous QPQ papers, we make a cut on velocity difference between the redshifts of the 
two quasars in a pair of $>3000\,{\rm km\,s^{-1}}$ to avoid physically associated binary quasars. 
The cut on velocity difference is motivated by the typical redshift uncertainty of 
$\approx500\,{\rm km\,s^{-1}}$. In QPQ8, it was required that the observed wavelengths of the 
metal ion transitions fall outside the Ly$\alpha$ forest of the background quasar. In this paper, 
we make a more aggressive Ly$\alpha$ forest cut. For stacked profile analysis, a good estimate of 
the continuum level is neessary. In QPQ8 we found that absorption associated to 
the foreground quasar occurs within $\pm2000\,{\rm km\,s^{-1}}$ around $z_{\rm fg}$. Therefore, it 
is desirable to keep a $\approx\pm3000\,{\rm km\,s^{-1}}$ window relatively free of contamination 
from Ly$\alpha$ forest. Taking into account the redshift uncertainty of the background quasar, 
we decide that at least one transition among \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
\ion{Mg}{2}\,2796) at $z_{\rm fg}$ should lie redward of 
$(1215.6701+20)\times(1+z_{\rm bg})\,{\rm \AA}$, for a pair to be included in the analysis.

Furthermore, we include only those spectra with average signal-to-noise (S/N) ratio exceeding 5.5 
per rest-frame \AA \ in a $\pm3000\,{\rm km\,s^{-1}}$ window centered on the observed wavelengths 
of the metal ion transitions. This criterion is a compromise between maximizing sample size versus 
maintaining good data quality on the individual sightlines. We find that S/N $>5.5$ per rest-frame 
\AA \ is 
necessary for properly estimating the continuum, as well as identifying mini-broad absorption line 
systems associated to the background quasar, which will significantly depress the flux level and 
bias the results. We also require that the $\pm2000\,{\rm km\,s^{-1}}$ window centered on the 
observed wavelengths of the metal ion transitions, where absorption associated to the foreground 
quasar is found, does not overlap with strong atmospheric ${\rm O}_2$ bands. The ${\rm O}_2$ 
A-band and B-band span 7595\textrm{--}7680\,AA \ and 6868\textrm{--}6926\,AA \ respectively.

In Table~\ref{tab:summ}, we list the sample size, the median redshift, and the median projected 
separation between the pair of the sub-samples that survive the above selection criteria for 
\ion{C}{2}\,1334, \ion{C}{4}\,1548, and \ion{Mg}{2}\,2796 respectively.

We then create composite spectra, that average over the intrinsic scatter in quasar environments, 
continuum placement errors, and redshift errors. The individual spectra 
of background quasars are shifted to the rest-frame of the foreground quasar at the transitions of 
interest. Each spectrum has been linearly 
interpolated onto a fixed velocity grid centered at $z_{\rm fg}$ with bins of 
$100\,{\rm km\,s^{-1}}$. For velocity bin of this size, it is unncessary to smooth the data to a 
common spectral resolution. The individual spectra are then combined with mean 
or median in a $\pm3000\,{\rm km\,s^{-1}}$ velocity window around $z_{\rm fg}$, where a velocity 
of $0\,{\rm km\,s^{-1}}$ corresponds to the wavelength of the metal ion transition at 
$z_{\rm fg}$. Bad pixels in the individual spectra have been masked before generating the 
composites. Since each quasar pair gives an independent probe of the CGM, each pair has an equal 
weighting in the stacked profiles. We do not weight the spectra by the measured S/N value of the 
metal ion transitions at $z_{\rm fg}$, since scatter in the stacked spectra is dominated by 
randomness in the CGM instead of error sources. The mean statistic of the individual spectra 
yields a good estimate of the average absorption and preserves equivalent width. On the other 
hand, a median statistic is less sensitive to outliers, however the averaged equivalent width is 
smaller and a measurement of the veloity width becomes more uncertain. We have stacked spectra 
using both the mean and the median statistic.

\section{Analysis}
\label{sec:analysis}

@@

JXP and MWL acknowledge support from the National
Science Foundation (NSF) grant AST-1010004 and AST-XX. 
JXP thanks the Alexander
von Humboldt foundation for a visitor fellowship to the MPIA where
part of this work was performed, as well as the staff at MPIA for
their hospitality during his visits.
JFH acknowledges generous support from the Alexander von Humboldt
foundation in the context of the Sofja Kovalevskaja Award. The
Humboldt foundation is funded by the German Federal Ministry for
Education and Research.

%Much of the data presented herein were obtained at the W.M. Keck
%Observatory, which is operated as a scientific partnership among the
%California Institute of Technology, the University of California, and
%the National Aeronautics and Space Administration. The Observatory was
%made possible by the generous financial support of the W.M. Keck
%Foundation.  Some of the Keck data were obtained through the NSF
%Telescope System Instrumentation Program (TSIP), supported by AURA
%through the NSF under AURA Cooperative Agreement AST 01-32798 as
%amended.
%
%Some of the data herein were obtained at the Gemini Observatory, which
%is operated by the Association of Universities for Research in
%%Astronomy, Inc., under a cooperative agreement with the NSF on behalf
%of the Gemini partnership: the NSF (United
%States), the Science and Technology Facilities Council (United
%Kingdom), the National Research Council (Canada), CONICYT (Chile), the
%Australian Research Council (Australia), Minist\'{e}rio da
%Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil) and Ministerio de
%Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina). 
%
%The authors wish to recognize and acknowledge the very
%significant cultural role and reverence that the summit of Mauna Kea
%has always had within the indigenous Hawaiian community. We are most
%fortunate to have the opportunity to conduct observations from this
%mountain.
%MWL thanks T.-K. Chan for a discussion on CGM simulations. MWL 
%thanks Chi Po Choi for a discussion on statistics.
